### 2018-12-09 Revision/Response/response.tex

\item \referee{p.3, line 36. I would call this the ``temperature exponent".}

\noindent The reviewer's suggestion has been incorporated in the revised manuscript on Page 3.

\item \referee{p.6, line 32. This is a spectral gap. Need to give credit to the
CSP community, although they consider spectral gaps in the nonlinear system,
while here the authors consider spectral gaps in C, which is related to the
system's response to varying model parameters.}

Thanks for this comment. As the referee notes, while the spectral 
truncations in active subspace methodology resemble aspects of CSP analysis,
the goals and approaches of these methods are substantially different. However, 
we are aware that CSP analysis is well-known in computational
chemistry community, and therefore, have included a brief mention 
of CSP in the introduction, clarifying the differences between 
the active subspace method and CSP.

@@

\item \referee{6.38: typo, $w_r$ should be $w_1$}

\noindent  The typo has been fixed in the revised manuscript.

\item \referee{7.23-27: why 'statistical independence' and not just 'independence'? Is there any other 
type of independence?}

\item \referee{7.29-30: Any PDF can be written in a Boltzmann form, V(x) is just the negative log-PDF, 
I am not sure if it is necessary to bring up a Boltzmann distribution language here.
Also, it could be confused with Maxwell-Boltzmann distribution, which is a very specific PDF form.}
Thanks for this comment. We followed the theory in ref [35] 
in the manuscript, where the authors derive Poincare type 
inequalities for functions of iid random
inputs distributed according to Boltzmann probability laws. 
We point out that the uniform distribution does not belong to this class. 
The required Poincare type inequality for the case of uniform 
distribution was derived in an earlier paper of Sobol' and Kucherenko (ref [34]). 
That
was the reason for assuming the distribution laws of the random inputs are
either \emph{uniform} or belong to the Boltzmann class, in section 3. An
important class of Boltzmann measures are the so called log-concave
distributions such as Normal, Exponential, Beta, and Gamma distributions. These
points have been clarified in the revised manuscript.

Additionally, we share the reviewer's concern about the potential confusions some readers
might face when seeing the mention of Boltzmann. We have removed the mention of
Boltzmann measures from the introduction, and now only refer to Boltzman
measures in Section
3, where the theoretical results are discussed.

### 2018-12-09 Revision/Paper/assa.tex
...
minor ..
the two comments ...

\section{GSA measures and their links with active subspaces}
\label{sub:gsa}
Consider a function $f = f(\xi_1, \xi_2, \ldots, \xi_\Np)$. 
While the active subspace framework described above does not make any assumptions
about statistical independence of the inputs $\xi_i$, $i = 1, \ldots, \Np$, 
the classical 
framework of variance based sensitivity analysis~\cite{Sobol:2001, Saltelli:2010} 
assumes that the inputs
are statistically independent. While extensions to the cases 
of correlated inputs exist~\cite{Borgonovo:2007,Li:2010,Jacques:2006,Xu:2007},
 we limit the discussion in this section to the
case of random inputs that are statistically independent and are 
either uniformly distributed or
distributed according to the Boltzmann probability distribution.
Note that a measure $\mu$
on $\R$ is referred to as a Boltzmann measure if it is 
absolutely continuous with respect to the Lebesgue measure  
and admits a density  of the form $\pi(x) = C \exp\{-V(x)\}$,
where $V$ is a continuous function and $C$ a normalization 
constant~\cite{Lamboni:2013}.

>>>>

\section{GSA measures and their links with active subspaces}
\label{sub:gsa}
Consider a function $f = f(\xi_1, \xi_2, \ldots, \xi_\Np)$. 
While the active subspace framework described above does not make any assumptions
about statistical independence of the inputs $\xi_i$, $i = 1, \ldots, \Np$, 
the classical 
framework of variance based sensitivity analysis~\cite{Sobol:2001, Saltelli:2010} 
assumes that the inputs
are statistically independent. While extensions to the cases 
of correlated inputs exist~\cite{Borgonovo:2007,Li:2010,Jacques:2006,Xu:2007},
 we limit the discussion in this section to the
case of random inputs that are statistically independent and are 
either uniformly distributed or
distributed according to the Boltzmann probability distribution.
Note that a measure $\mu$
on $\R$ is referred to as a Boltzmann measure if it is 
absolutely continuous with respect to the Lebesgue measure  
and admits a density  of the form $\pi(x) = C \exp\{-V(x)\}$,
where $V$ is a continuous function and $C$ a normalization 
constant~\cite{Lamboni:2013}. \rebut{
An important class of Boltzmann distributions are the so called log-concave
distributions, which include Normal, Exponential, Beta, Gamma, Gumbel, and
Weibull distributions. Note also that the uniform distribution does not fall under
the class of Boltzmanm distributions.~\cite{Lamboni:2013}.}

### 2018-12-09 Revision/Paper/intro.tex
the two comments ...

In complex mechanisms involving a large number of reactions, characterizing the
propagation of uncertainty from a large set of inputs to the model output is
challenging due to the associated computational effort.  A major focus of this
article is the implementation of a robust framework that aims to identify
\emph{important} directions in the input space that predominantly capture the
variability in the model output. These directions, which constitute the so called
\emph{active subspace}~\cite{Constantine:2015}, are the dominant eigenvectors
of a matrix derived from the gradient information of the model output with
respect to an input. The active subspace methodology thus focuses on reducing
the dimensionality of the problem, and hence the computational effort
associated with uncertainty propagation.

>>>>

In complex mechanisms involving a large number of reactions, characterizing the
propagation of uncertainty from a large set of inputs to the model output is
challenging due to the associated computational effort.  A major focus of this
article is the implementation of a robust framework that aims to identify
\emph{important} directions in the input space that predominantly capture the
variability in the model output. These directions, which constitute the so called
\emph{active subspace}~\cite{Constantine:2015}, are the dominant eigenvectors
of a matrix derived from the gradient information of the model output with
respect to an input. The active subspace methodology thus focuses on reducing
the dimensionality of the problem, and hence the computational effort
associated with uncertainty propagation. The focus here is on input parameter
dimension reduction. \rebut{This is different from 
techniques such at Computational
Singular Perturbation (CSP)~\cite{GoussisLam92,FotacheKreutzLaw97,
Lam85,LamGoussis89,ValoraniCretaGoussisEtAl06,
DebusschereMarzoukNajmEtAl12,
SalloumAlexanderianLeMaitreEtAl12,
GuptaImValorani13} that aim to reduce the
complexity of stiff chemical systems by filtering out the 
fast timescales from the system. The latter is done, for instance, using
the eigenvectors of the system Jacobian 
to decouple the fast and slow processes; see e.g.,~\cite{DebusschereMarzoukNajmEtAl12}.}
